Viscous Transport in Eroding Porous Media

### 2019-08-01 docs/transport/erosion_transport.tex
modify figures in transport paper
worked on numerical results

There have been efforts to relate the tortuosity to the
porosity~\cite{matyka2008tortuosity}, but these results can not be
universal since the porosity which depends on only a single number, the
tortuosity is affected by the distribution of pores within the porous
network.  In addition to the hydraulic tortuosity, a local tortuosity
can be used to analyze the local behavior of a streamline near a
body~\cite{matyka2008tortuosity}.  The local tortuosity of a streamline
initialized at $y$ along $S$ is
\begin{align*}
  \tau(y) = \frac{\lambda(y)}{d}.
\end{align*}
\todo[inline]{Need to flesh this out more}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{A Single Body Close to a Wall}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We consider a single eroding body close to a solid wall.  To compare our
results with a similar numerical experiment performed by Mitchell and
Spagnolie~\cite{mit-spa2017}, rather a pressure drop boundary condition,
we impose the shear flow
\begin{align}
  \UU(\xx)=\left[
  \begin{array}{c}
    y+1 \\ 0
  \end{array}
  \right],
\end{align}
on the outer wall.  In their experiment, Mitchell and Spagnolie place
the center of the eroding body $1.5$ times the body's radius above the
solid wall.  By using the Barycentric quadrature rule described in
Section~\ref{sec:bary} rather than the trapezoid rule, the eroding body
can be placed much closer to the solid wall without requiring an
unreasonable number of discretization points.  We consider an eroding
body that is initially a circle of radius $r=0.4$ and is placed near the
no-slip wall at $y=-1$.  We discretize the eroding body with
$N_\iin=256$ discretization points, and the center of the eroding body
is initially chosen so that the distance between the body and the solid
wall are $h/2$, $h/4$, and $h/10$, where $h = 2\pi r/N_\iin$.  For all
three simulations, we use the time step size $\Delta t=10^{-4}$.

In Figure~\ref{fig:NearWall}, we superimpose the eroding body's shape at
several equispaced time steps.  For the three initial configurations,
the shear stress is positive for all time, but varies over several
orders of magnitude.  Therefore, we color eroding body's boundary
according to the logarithm of the shear stress.  Comparing our results
to Mitchell and Spagnolie~\cite{mit-spa2017} (Figure 7(c)), we see that
the body shapes are similar.  The differences we can attribute to our
assumption of a two-dimensional flow.  In three dimensions, there is no
recirculation between the solid wall and the spherical
body~\cite{cha-feu2003}.  In contrast, between a two dimensional
circular body and a solid wall, there are regions of recirculation on
the fore and aft sides of the body.  In Figure~\ref{fig:NearWall_vort},
we plot the vorticity at the final configuration, and the where the
vorticity is smallest corresponds to the region where there is a slow
recirculation.

Since the shear stress is always positive, the erosion rate is a smooth
function and does not lead to the development of corners.  However,
since the location where the shear stress is minimized is close to
regions of high shear stress, the rate of erosion changes quickly, and
the result is a body that seems to be developing a corner, although it
is not.  Similar to the three dimensional case~\cite{mit-spa2017}, this
region of high curvature develops in the top half of the eroding body.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r1h_shear}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r0d5h_shear}
\includegraphics[width = 0.38 \textwidth]{./figs/1b_0d4r0d1h_shear}
\caption{\label{fig:NearWall} 
  A single body eroding in a Stokes flow. The color denotes the
  logarithm of the shear stress on the body. Therefore, erosion is
  fastest in the red regions (top half)and slowest in the blue regions
  (lower half).  The body is initialized at three different distances
  from the lower wall: $d=h$ (left), $h/2$ (middle), and $h/10$
  (right).}
\end{center}
\end{figure}
\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r1h_vort}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r0d5h_vort}
\includegraphics[width = 0.33 \textwidth]{./figs/1b_0d4r0d1h_vort}
\caption{\label{fig:NearWall_vort} The vorticity of the fluid with a single body eroding 
at time t=0.1001. The initial distances from body to wall are $h$ (left), $h/2$
  (middle), and $h/10$ (right).  }
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{20 nearly touching bodies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We consider 20 eroding bodies initially placed in $[-1,1] \times
[-1,1]$.  The background flow is the Hagen-Poiseuille flow
\begin{align}
  \UU(\xx)=U \left[
  \begin{array}{c}
    1-y^2 \\ 0
  \end{array}
  \right],
\end{align}
where the flow rate $U$ is chosen so that the pressure drop from $x=-2$
to $x=2$ is held fixed at 2.  We start by analyzing the effect of
erosion on the area fraction and the flow rate.  In
Figure~\ref{fig:Eroding20flowrate}(a), we plot the area fraction as a
function of normalized time.  Initially, 62\% of the geometry is eroded
bodies corresponding to a porosity of $0.38$, and the area fraction
decreases to 0 as the bodies erode.  The trend of the area fraction
resembles that of our previous work~\cite{qua-moo2018} (Figure 10(a)),
but with a larger initial area fraction.  We also compute the flow rate
$U$ required to maintain a constant pressure drop across the channel in
Figure~\ref{fig:Eroding20flowrate}(b).  Again, the trend of $U$
resembles that of our previous work~\cite{qua-moo2018} (Figure 10(b)),
except that the initial flow rate is an order of magnitude smaller
because of the larger initial area fraction.  Starting around normalized
time $0.2$, Figure~\ref{fig:Eroding20flowrate}(b) is roughly linear
which indicates that the flow rate can be written as a power law.  Using
a line of best fit, the flow rate is approximately \begin{align} U
\approx \left(\frac{t}{t_f}\right)^{15/4}, \end{align}
\todo[inline]{update this with whatever S-H gets} which is the dashed
line in Figure~\ref{fig:Eroding20flowrate}(b).

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/porosity20dense_new}
\todo[inline]{SH: Make the y-limits of this figure go from 0 to 0.7 ...
no need to make it go below 0. Done 07312019}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/flow_rate20dense}
\todo[inline]{SH: In this figure, can you superimpose a line of best fit
from about normalized time 0.2 to normalize time 1.  Doing this crudely,
I got a slope of 15/4}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20flowrate}(a): The area fraction of 20
nearly touching eroding bodies versus normalized time. (b): The incoming
flow rate, $U$, for a fixed pressure drop across the channel versus
normalized time.  The flow rate is initially very small, but it
eventually increases as a power law (dashed line) towards the flow rate
$U=1$ that occurs once all the bodies have eroded.}
\end{figure}

Snapshots of the bodies at four equispaced times are shown in
Figure~\ref{fig:Eroding20vort}.   The colormap is the vorticity which is
equivalent to the shear stress when restricted to the eroding bodies.
Therefore, erosion is fastest in regions where the magnitude of the
vorticity is largest.  Initially, several of the eroding bodies are
close to the outer wall.  In particular, with $h=L_2/N_\out$, the
distance between bodies 1, 6, 13, and 15 are $1.3h$, $2.9h$, $2.8h$, and
$1.3h$, respectively.  In addition, since each body is discretized with
$N_\iin=256$ points, the distance between several pairs of eroding
bodies is too small to be accurately resolved with the trapezoid rule at
the prescribed resolution.  Particular pairs include bodies 1 \& 6, 3 \&
9, 6 \& 8, and 14 \& 18.  By using the Barycentric quadrature rule, the
interaction between these nearly-touching bodies can be accurately
resolved at the prescribed resolution.

\begin{figure}[H]
\begin{center}
  \includegraphics[height=0.22\textwidth]{./figs/20b_dense1}
  \includegraphics[height=0.22\textwidth]{./figs/20b_dense101}
  \includegraphics[height=0.22\textwidth]{./figs/20b_dense201}
  \includegraphics[height=0.22\textwidth]{./figs/20b_dense301_new}
  \todo[inline]{S-H: Increase the font of the colorbar.   DONE 07312019}
\caption{\label{fig:Eroding20vort} Erosion of 20 nearly touching bodies
with the fixed pressure drop condition. The color is the vorticity of
the fluid. The 4 snapshots are evenly spaced in time. We use $N_\iin =
256$ discretization points on the body, a time-step of $\Dt=10^{-4}$,
and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $. In the
forth frame, bodies 4, 12, and 17 have vanished completely, and body 19
has almost completely eroded.}
\end{center}
\end{figure}

In~\cite{qua-moo2018}, we observed that erosion causes the space between
nearly touching bodies to quickly expand, and flat faces develop along
the region of near contact.  This qualitative behavior is also observed
in Figure~\ref{fig:Eroding20vort}, such as between bodies 3 \& 4 and 15
\& 16.  However, by resolving bodies that are much closer to one another
when compared to our previous work~\cite{qua-moo2018}, we see that it is
possible for very little erosion to occur between a pair of bodies.  In
particular, for pairs of bodies where the channel between the bodies is
nearly perpendicular to the main flow direction (bodies 1 \& 6, 3 \& 9,
and 5 \& 13), there is very little shear stress and the effect of
erosion is slight.

In this example, we also observe that erosion creates a network of
channels from the inlet to outlet where the velocity and vorticity, and
therefore erosion rate, are much larger than the other regions.  These
channels can be further visualized by considering the streamlines.  In
Figure~\ref{fig:Eroding20tracer}, we freeze the geometry at the second
time step in Figure~\ref{fig:Eroding20vort}, and we simulate 200
tracers.  The tracers are initially placed at $x=-1$ and equispaced in
$y$.  There are two clear region where the tracers pass through the
geometry much faster than the other regions.  One of these fast regions
is located between the bodies and the solid wall at $y=1$, and the other
cuts through the porous region with the upper part of the channel formed
by bodies 1, 4, 6, and 8.  To illustrate the ability of the Barycentric
quadrature formula, streamlines very close to the eroding bodies are
illustrated in the last frame of Figure~\ref{fig:Eroding20tracer}.

\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b30}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b90}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b150}\\
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b210}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270_zoom}
\caption{\label{fig:Eroding20tracer}The trajectories of 200 tracers in
the fluid with 20 bodies. The five first snapshots are evenly spaced in
time.  The tracers are evenly spread in the $y$-direction and released
at $x=-1$. The bottom right frame is a zoom window of the bottom middle
frames.  Since we use a Barycentric quadrature rule and the fourth order
Runge Kutta method, the tracers can be very close to but not penetrate
the bodies.}
\end{center}
\end{figure}

{\color{red} 
Besides the channels between two bodies, there is a single channel goes
across the domain horizontally and the flow has been concentrated in
this channel.  In the second frame of Fig.~\ref{fig:Eroding20vort}, this
channel is between bodies 1 \& 20, 1 \& 9, 4 \& 3, 8 \& 11, 8 \& 2, 6 \&
12, and 6 \& 19.  We can get a better understanding of this channel from
the trajectories of tracers in Fig.~\ref{fig:Eroding20tracer}.  In Fig.~\ref{fig:Eroding20tracer}, 
the flow (or tracer) first comes from three small channels between outer wall \& body
10, bodies 7 \& 14, and bodies 14 \& 18, then the three branches become
one and go into the main channel between bodies 1 \& 9.  From the first
frame to the forth frame of Fig.~\ref{fig:Eroding20vort}, this channel
is expanding faster than other channel and bodies 4 \& 12 has vanished
and body 19 is almost gone in the forth frame.  The reason of fast
expansion of this channel is the high vorticity.  In the forth frame of
Fig.~\ref{fig:Eroding20vort}, we could see the vorticity is relatively
high on the side of bodies which form this channel so the bodies are
eroded fast on the side of this channel or have vanished completely.

Furthermore, how long the body lasts in the fluid depends on not only the size of
the body but also the location of the body.  For example, the first
three vanishing bodies are body 12 (as t=0.0256), 4 (as t=0.0278), then
17 (as t=0.0287).  Since body 4 is located in the main flow channel so
the body 4 is vanished earlier than body 17 although the initial size of
body 4 is larger than the size of body 17.  This channel will keep
expanding and the bodies around this channel will vanish earlier than
others.  After body 17, the next 8 vanished bodies with respect to time
are body 19 (as t=0.0312),  body 7 (as t=0.0325), body 20 (as t=0.0329),
body 8 (as t=0.0349), body 10 (as t=0.0353), body 3 (as t=0.0356), body
14 (as t=0.0363), then body 9 (as t=0.0376).  All of these eight bodies
were around this channel before they are gone.

For the flat faces at the sites of near contact, since we put the body
be close to one another so we are able to see all the channels between
two close bodies have flat faces.  Besides the channels between bodies,
we also observe the flat faces on the bodies which are close to the
outer wall. For example, we see the flat faces on the top of bodies 1 \&
6 and the bottom of bodies 13 \& 15.

Since we use a Barycentric quadrature rule to approximate the velocity
of tracers and apply the fourth order Runge Kutta method to find the new
locations of tracers in each step, the tracers can be very close to but
not penetrate the bodies.  Those body-closed tracers are moving
perfectly so we are able to observe the details of the interaction of
bodies and fluid.  Although the direction of flow is from left to right,
the tracers will not only travel horizontally but also vertically.  In
the bottom middle frame of Fig.~\ref{fig:Eroding20tracer}, some tracers
climb up from right to left around the body.  There is a zoom windows of
the climbing tracers trajectories in the bottom right frame of Fig.~\ref{fig:Eroding20tracer} and
they are taken from the bottom middle frame of
Fig.~\ref{fig:Eroding20tracer} with more tracers.  In the bottom right frame of 
Fig.~\ref{fig:Eroding20tracer} the tracers around the center body first go
from the channel below the body, climb up to the left, then go to the
right and join another tracers in the channel above the body. 
}
%\begin{figure}[H]
%\begin{center}
%\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b210_zoom}
%\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b240_zoom}
%\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b270_zoom}
%\caption{\label{fig:Eroding20zoom}The zoom windows in the last three
%  frames of Figure~\ref{fig:Eroding20tracer}. The trajectories of
%  tracers around the bodies. Since we use a Barycentric quadrature rule
 % and the fourth order Runge Kutta method, the tracers can be very close
 % to but not penetrate the bodies.}
%\end{center}
%\end{figure}

\begin{figure}[H]
\begin{subfigure}[b]{0.45\textwidth}
\begin{subfigure}[b]{\textwidth}
\includegraphics*[width =\linewidth]{./figs/velocity_loc20_268}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
\includegraphics*[width =\linewidth]{./figs/tort_local20_268}
\caption{}
\end{subfigure}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/tort_diff_top10_268}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20tort} The tortuosity study in the fluid with 
20 nearly touching bodies when the porosity is 62.9 \%.
(a) The 
x-component velocity u(-1, y) with respect to its maximum velocity
$u_{\max}=2.9828
\times 10^{-3}$ at equal spreading tracers on the cross section x = -1. 
(b) The local tortuosity $\tau(y)$ on the cross section x = -1. 
(c) The largest 10 difference of 
local tortuosity $\tau$ at two neighboring tracers in
 20 nearly touching bodies eroding when the porosity is 62.9 \% 
and the tortuosity is 1.0979. The same color of a pair of trajectories 
means they are from two neighboring tracers.}
%(c) The difference of $\tau(y)$ at two neighboring tracers on the cross section x = -1.
%(d) The ratio of the minimum to maximum speeds along the trajectories of tracers.}
\end{figure}

{\color{red}
In Fig.~\ref{fig:Eroding20tort} we release 1000 tracers 
from the starting cross section x = -1 to 
the end cross section x = 1 and 
use the local tortuosity to analysis the effect
of the geometrical structure on fluid velocity field when the porosity is 62.9 \%.
In Fig.~\ref{fig:Eroding20tort}(a) the graph represents the ratio of the
x-component velocity u(-1, y) to its maximum velocity $u_{max}=2.9828
\times 10^{-3}$ at equal spreading tracers on the starting cross section.
The velocity is continuous along the starting cross section and
acting as several Poiseuille flows. This velocity graph is different
from the one in~\cite{matyka2008tortuosity} since we choose our cross
section to be the beginning of the flow before the fluid touches any
body. In Fig.~\ref{fig:Eroding20tort}(b) we record the local tortuosity
$\tau(y)=\lambda(y)/d$
of the tracers at $y$ on the starting cross section x = -1 
where $d = 2$.
This graph is not continuous 
and the jumps in $\tau$ mean that the initial neighboring tracers have been
seperated by the bodies. 
The maximum of $\tau$ is 1.2713 and the minimum is 1.0001.
}

{\color{red}
In Fig.~\ref{fig:Eroding20tort}(c) we calculate the difference of 
$\tau$ at two neighboring tracers 
and draw the trajectories of neighboring tracers
if the difference of $\tau$ at the neighboring tracers is large. 
From Fig.~\ref{fig:Eroding20tort}(c), we collect the 10 largest difference of $\tau$ 
at the neighboring tracers and 
draw the pair of trajectories in the same color and 
are able to tell the neighboring trajectories will be very 
different if they are separated by bodies.
For each pair of trajectories, 
they are splitted by the body at the left side of the body, then
one of them goes up and the other one goes down along the body 
until they rejoin with each other at the right side of body.  
Furthermore, the pair trajectories could be splitted by more than one body, 
for example in Fig.~\ref{fig:Eroding20tort}(c) the toppest red pair trajectories 
are splitted by two close bodies.
}

>>>>

There have been efforts to relate the tortuosity to the
porosity~\cite{matyka2008tortuosity}, but these results can not be
universal since the porosity which depends on only a single number, the
tortuosity is affected by the distribution of pores within the porous
network.  In addition to the hydraulic tortuosity, a local tortuosity
can be used to analyze the local behavior of a streamline near a
body~\cite{matyka2008tortuosity}.  The local tortuosity of a streamline
initialized at $y$ along $S$ is
\begin{align}
  \tau(y) = \frac{\lambda(y)}{d}.
  \label{eqn:localTort}
\end{align}
\todo[inline]{Need to flesh this out more}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{A Single Body Close to a Wall}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We consider a single eroding body close to a solid wall.  To compare our
results with a similar numerical experiment performed by Mitchell and
Spagnolie~\cite{mit-spa2017}, rather than a pressure drop boundary
condition, we impose the shear flow
\begin{align}
  \UU(\xx)=\left[
  \begin{array}{c}
    y+1 \\ 0
  \end{array}
  \right],
\end{align}
on the outer wall.  In their experiment, Mitchell and Spagnolie place
the center of the eroding body $1.5$ times the body's radius above the
solid wall.  By using the Barycentric quadrature rule described in
Section~\ref{sec:bary} rather than the trapezoid rule, the eroding body
can be placed much closer to the solid wall without requiring an
unreasonable number of discretization points.  We consider an eroding
body that is initially a circle of radius $r=0.4$.  We discretize the
eroding body with $N_\iin=256$ discretization points, and its center is
chosen so that the distance between the body and the solid wall is
$h/2$, $h/4$, and $h/10$, where $h = 2\pi r/N_\iin$.  For all three
simulations, we use the time step size $\Delta t=10^{-4}$.

In Figure~\ref{fig:NearWall}, we superimpose the eroding body's shape at
equispaced time steps.  For the three initial configurations, the shear
stress is positive for all time, but varies over several orders of
magnitude.  Therefore, we color the eroding body's boundary with the
logarithm of the shear stress.  Since the shear stress is always
positive, the erosion rate is a smooth function and does not lead to the
development of corners.  However, the shear stress varies over several
orders of magnitude, and this leads to interesting shapes.  For
instance, in the top hemisphere, there is a sudden increase in the shear
stress, and this leads to a region of high curvature.  This behavior is
also present in three dimensions~\cite{mit-spa2017} (Figure 7(c)).  The
biggest difference between the two- and three-dimensional results is the
presence of a recirculation zone.  In three dimensions, there is no
recirculation between the solid wall and the spherical
body~\cite{cha-feu2003}.  In contrast, the two-dimensional flow Stokes
flow can have recirculation zones~\cite{chw-wu1975, hig1985}. To
visualize the flow, we plot the vorticity of the final time step from
Figure~\ref{fig:NearWall} in Figure~\ref{fig:NearWall_vort}.  The region
where the vorticity is smallest corresponds to the recirculation region.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r1h_shear}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r0d5h_shear}
\includegraphics[width = 0.38 \textwidth]{./figs/1b_0d4r0d1h_shear}
\caption{\label{fig:NearWall} 
  A single body eroding in a Stokes flow. The color denotes the
  logarithm of the shear stress on the body. Therefore, erosion is
  fastest in the red regions (top half)and slowest in the blue regions
  (lower half).  The body is initialized at three different distances
  from the lower wall: $d=h$ (left), $h/2$ (middle), and $h/10$
  (right).}
\end{center}
\end{figure}
\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r1h_vort}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r0d5h_vort}
\includegraphics[width = 0.33 \textwidth]{./figs/1b_0d4r0d1h_vort}
\caption{\label{fig:NearWall_vort} The vorticity of the fluid with a single body eroding 
at time t=0.1001. The initial distances from body to wall are $h$ (left), $h/2$
  (middle), and $h/10$ (right).  }
\end{center}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{20 nearly touching bodies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We consider 20 eroding bodies that are discretized with $N_\iin=256$
points and are initially placed in $[-1,1] \times [-1,1]$.  The
background flow is the Hagen-Poiseuille flow
\begin{align}
  \UU(\xx)=U \left[
  \begin{array}{c}
    1-y^2 \\ 0
  \end{array}
  \right],
\end{align}
where the flow rate $U$ is chosen so that the pressure drop from $x=-2$
to $x=2$ is held fixed at 2.  We start by analyzing the effect of
erosion on the area fraction and the flow rate.  In
Figure~\ref{fig:Eroding20flowrate}(a), we plot the area fraction as a
function of normalized time.  Initially, 62\% of the geometry is eroded
bodies corresponding to a porosity of $0.38$, and the area fraction
decreases to 0 as the bodies erode.  The trend of the area fraction
resembles that of our previous work~\cite{qua-moo2018} (Figure 10(a)),
but with a larger initial area fraction.  We also compute the flow rate
$U$ required to maintain a constant pressure drop across the channel in
Figure~\ref{fig:Eroding20flowrate}(b).  Again, the trend of $U$
resembles that of our previous work~\cite{qua-moo2018} (Figure 10(b)),
except that the initial flow rate is an order of magnitude smaller
because of the larger initial area fraction.  Starting around normalized
time $0.2$, Figure~\ref{fig:Eroding20flowrate}(b) is roughly linear
which indicates that the flow rate can be written as a power law.  Using
a line of best fit, the flow rate is approximately 
\begin{align} 
  U \approx \left(\frac{t}{t_f}\right)^{3.43},
\end{align}
which is the dashed line in Figure~\ref{fig:Eroding20flowrate}(b).

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/porosity20dense}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.51\textwidth}
\includegraphics*[width =\linewidth]{./figs/flow_rate20dense}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20flowrate}(a): The area fraction of 20
nearly touching eroding bodies versus normalized time. (b): The incoming
flow rate, $U$, for a fixed pressure drop across the channel versus
normalized time.  The flow rate is initially very small, but it
eventually increases as a power law (dashed line) towards the flow rate
$U=1$ that occurs once all the bodies have eroded.}
\end{figure}

Snapshots of the bodies at four equispaced times are shown in
Figure~\ref{fig:Eroding20vort}.  The color is the vorticity which is
equivalent to the shear stress when restricted to the eroding bodies.
Therefore, erosion is fastest in regions where the magnitude of the
vorticity is largest.  Initially, several of the eroding bodies are
closer to the outer wall than the $5h$ threshold required to guarantee
sufficiently accurate quadrature with the trapezoid rule.  In
particular, with $h=L_2/N_\out$, the distance between bodies 1, 6, 13,
and 15 are $1.3h$, $2.9h$, $2.8h$, and $1.3h$, respectively.  In
addition, the distance between several pairs of eroding bodies is too
small to be accurately resolved with the trapezoid rule at the
prescribed resolution.  Particular pairs include bodies 1 \& 6, 3 \& 9,
6 \& 8, and 14 \& 18.  By using the Barycentric quadrature rule, the
interaction between these nearly-touching bodies can be accurately
resolved at the prescribed resolution.

\begin{figure}[H]
\begin{center}
  \includegraphics[height=0.225\textwidth]{./figs/20b_dense1}
  \includegraphics[height=0.225\textwidth]{./figs/20b_dense101}
  \includegraphics[height=0.225\textwidth]{./figs/20b_dense201}
  \includegraphics[height=0.225\textwidth]{./figs/20b_dense301}
\caption{\label{fig:Eroding20vort} Erosion of 20 nearly touching bodies
with the fixed pressure drop condition. The color is the vorticity of
the fluid. The 4 snapshots are evenly spaced in time. We use $N_\iin =
256$ discretization points on the body, a time-step of $\Dt=10^{-4}$,
and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $. In the
forth frame, bodies 4, 12, and 17 have vanished completely, and body 19
has almost completely eroded.}
\end{center}
\end{figure}

In~\cite{qua-moo2018}, we observed that erosion causes the space between
nearly touching bodies to quickly expand, and flat faces develop along
the region of near contact.  This qualitative behavior is present in
Figure~\ref{fig:Eroding20vort} between bodies 3 \& 4, 15 \& 16, and
others.  However, now that we can resolve bodies that are much closer
together, we observe that, at least initially, very little erosion
occurs between certain pairs of bodies.  For instance the opening
between bodies 1 \& 6 grows much slower than the opening between bodies
15 \& 16.  A common feature of the openings that grow slowly is that
they are nearly perpendicular to the main flow direction, and this
results in very low erosion because of the small shearing.  For example,
the openings between the pair of bodies 1 \& 6, 3 \& 9, and 5 \& 13.

In this example, we also observe that erosion creates a network of
channels from the inlet to outlet where the velocity and vorticity, and
therefore erosion rate, are much larger than the other regions.  These
channels can be further visualized by considering the streamlines.  In
Figure~\ref{fig:Eroding20tracer}, we freeze the geometry at the second
time step from Figure~\ref{fig:Eroding20vort}, and we simulate 200
tracers.  The tracers are initially placed at $x=-1$ and are equispaced
in $y$.  The trajectories are shown at 5 different times, and the final
plot is a zoom in of the lower right quadrant of the fifth time step.
There are three clear regions where the tracers pass through the
geometry fastest.  Two of these regions are located between the bodies
and the solid walls at $y=\pm 1$, and the third cuts through the porous
region with the upper part of the channel formed by bodies 1, 4, 6, and
8.  Since the flow is fastest in these regions, the shearing is largest,
and this causes these openings to grow fastest which can be observed in
Figure~\ref{fig:Eroding20vort}.

\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b30}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b90}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b150}\\
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b210}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270_zoom}
\caption{\label{fig:Eroding20tracer}The trajectories of 200 tracers in
the second geometry from Figure~\ref{fig:Eroding20vort}. The tracers are
initialized at $x=-1$ and are evenly spaced in the $y$-direction. The
first five snapshots are evenly spaced in time.  The bottom right frame
is a zoom window of the fifth snapshot.  Since we use a Barycentric
quadrature rule and the fourth-order Runge-Kutta method, the tracers can
be very close to but not penetrate the bodies.}
\end{center}
\end{figure}

Next, we use the tracer trajectories to compute the anomalous diffusion
rates and the tortuosities in the eroding geometry.  Since these
calculations use a statistical analysis of the tracer trajectories, we
increase the number of trajectories to $N_p = 1000$.  Again, the tracers
are initialized at $x=-1$, and their $y$ coordinates are distributed
evenly across the entire channel.  To compute the tortuosity, we
require the velocity at the initialization points of the tracers.  These
normalized velocities are plotted in Figure~ref{fig:Eroding20tort}(a)
for the eroded geometry with porosity 62.9\% (see
Figure~\ref{fig:Eroding20tort}(c)).  The velocities are similar to the
work of Matyka et al.~\cite{matyka2008tortuosity} (see Figure 4(a)),
except that our cross-section does not cut through any of the bodies.
Next, in Figure~\ref{fig:Eroding20tort}(b), we plot the local
tortuosity~\eqref{eqn:localTort} by calculating the length of each
trajectory as it traverses the channel from $x=-1$ to $x=1$ in
Figure~\ref{fig:Eroding20tort}(b), and dividing by the length of the
channel.  The local tortuosity ranges from 1 to 1.27, meaning that one
of the tracers travelled 27\% farther than it would have if the bodies
had been absent.  The average tracer travelled 9.79\% farther than if
the bodies had been absent, meaning that the tortuosity of the eroded
channel is $1.098$.  Again, comparing the local tortuosity to
Matyka~\cite{matyka2008tortuosity} (Figure 4(b)), the results are
qualitatively similar. However, since our initial cross-section does not
cut through any bodies, the local tortuosity does not have any gaps.
The discontinuities correspond to neighboring tracers with one traveling
much farther than the other.  In Figure~\ref{fig:Eroding20tort}(c), we
plot pairs of trajectories that correspond to the ten largest jumps in
the local tortuosity.  Corresponding pairs are always plotted in the
same color.  The discrepancy between the trajectory lengths can be
attributed to the tracers diverging from one another as they approach
opposite sides of a stagnation point in the flow.

\begin{figure}[H]
\begin{subfigure}[b]{0.45\textwidth}
\begin{subfigure}[b]{\textwidth}
\includegraphics*[width =\linewidth]{./figs/velocity_loc20_268}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
\includegraphics*[width =\linewidth]{./figs/tort_local20_268}
\todo[inline]{S-H: Can cut the ylimit at 1.3}
\caption{}
\end{subfigure}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/tort_diff_top10_268}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20tort} The tortuosity of an eroded geometry
with porosity 62.9\%. (a) The x-component of the velocity $u(-1, y)$
normalized by its maximum velocity of $2.98 \times 10^{-3}$. (b) The
local tortuosity $\tau(y)$ on the cross section $x = -1$.  The spatially
averaged tortuosity through the channel is $1.098$.  (c) The
trajectories resulting in the ten largest differences between
neighboring trajectories.  Neighboring trajectories have the same
color.}
\end{figure}
